What if you drop that? Developmental changes in curiosity about physical interactions

### 2021-01-15 paper/paper2021.Rmd
authors

author-information: > 
    \author{{\large \bf George Kachergis (kachergis@stanford.edu)} \and {\large \bf Sama Radwan} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94305 USA
    \AND {\large \bf Judith Fan (jefan@ucsd.edu)} \\ Department of Psychology, University of San Diego \\ Madison, WI 53706 USA
    \AND {\large \bf Dan Yamins} \\ Departments of Psychology & Computer Science, Stanford University \\ Palo Alto, CA 94305 USA
    \AND {\large \bf Michael C.~Frank} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94305 USA}

>>>>

author-information: > 
    \author{{\large \bf George Kachergis (kachergis@stanford.edu)} \and {\large \bf Sama Radwan} \and {\large \bf Bria Long} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94305 USA
    \AND {\large \bf Judith Fan (jefan@ucsd.edu)} \\ Department of Psychology, University of San Diego \\ Madison, WI 53706 USA
    \AND {\large \bf Daniel Bear} \and {\large \bf Daniel Yamins} \\ Departments of Psychology & Computer Science, Stanford University \\ Palo Alto, CA 94305 USA
    \AND {\large \bf Michael C.~Frank} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94305 USA}
